---
title: "01 Tidyverse"
author: "Muhammad Shamookh"
date: "2024-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Tidyverse
Last compiled: `r Sys.Date()`

Throughout the chapter, I gained proficiency in the fundamental aspects of the tidyverse library, encompassing essential skills in both data wrangling and data visualization.

# Challenge No. 01
Utilizing the **'bike_orderlines_wrangled_tbl'** dataset and the acquired knowledge, I derived the 'state' and 'city' columns for grouping solely by the 'state' variable. Later, I visualized sales by states through a bar plot, to attain further insights into their relationship.

## Sales by State
```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)

# 2.0 Importing Files ----
bike_orderlines_wrangled_tbl <- read_rds("01_tidyverse_files/bike_orderlines.rds")

# 3.0 Examining Data ----
#bike_orderlines_wrangled_tbl %>%
#head(bike_orderlines_wrangled_tbl, n=7)

# 4.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col = location,
           into = c("city", "state"),
           sep = ", ")

# 5.0 Business insight ----
#5.1 Challenge No. 1 - Sales by State ----

#Step 1 - Manipulate----
sales_by_state <- bike_orderlines_wrangled_tbl %>%
  select(state, total_price) %>%
  group_by(state) %>%
  summarize(sales = sum(total_price))
sales_by_state %>% head(n=10)

#Step 2 - Visulaize----
plot_1 <- sales_by_state %>%
  ggplot(aes(x = state, y = sales),)+
  geom_col(fill = "blue")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = "Sales By State")+
  labs(y = "Sales")+labs(x = "States")+
  theme(plot.title = element_text(size = 34))+
  theme(axis.title.x = element_text(size = 28))+
  theme(axis.title.y = element_text(size = 28))+
  theme(axis.text.y = element_text(size = 14))+
  theme(axis.text.x = element_text(size = 14))+
  theme(text = element_text(family = "Times New Roman"))+
  theme(axis.title = element_text(face="bold"))+
  theme(axis.text = element_text(face="bold"))+
  theme(plot.title = element_text(face="bold"))+
  theme(axis.title.x=element_text(colour="black"))+
  theme(axis.title.y=element_text(colour="black"))+
  theme(axis.text.x=element_text(colour="black"))+
  theme(axis.text.y=element_text(colour="black"))+
  theme(plot.title=element_text(hjust=0.5))

plot_1
ggsave("01_tidyverse_files/figure-html/sales_by_state.png", height = 7 , width = 12)
```

**The above figure illustrates that North Rhine-Westphalia has the highest revenue among all states.**


# Challenge No. 02

By utilizing the **'bike_orderlines_wrangled_tbl'** dataframe, applying grouping based on the 'state' and 'year' column. Subsequently, then visualized the sales distribution across different states over the years, employing a bar plot with facets arranged by state using **'facet_wrap(~state)'**.


## Sales by State by Year

```{r}

# 5.2 Challenge No. 2 - sales by location and year (facet_wrap) ----

#Step 1 - Manipulate----
sales_by_state_by_year <- bike_orderlines_wrangled_tbl %>%
  select(state, total_price, order_date) %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>%
  summarize(sales = sum(total_price), state = state)
sales_by_state_by_year %>% head(n=5)


#Step 2 - Visulaize----
plot_2 <- sales_by_state_by_year %>%
  ggplot(aes(x = year, y = sales, fill = state)) +
  facet_wrap(~state) +
  geom_col(fill = "chocolate2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = "Sales By Location and Year")+
  labs(x = "Year")+
  labs(y = "Sales")+
  theme(plot.title = element_text(size = 34))+
  theme(axis.title.x = element_text(size = 28))+
  theme(axis.title.y = element_text(size = 28))+
  theme(axis.text.y = element_text(size = 14))+
  theme(axis.text.x = element_text(size = 14))+
  theme(text = element_text(family = "Times New Roman"))+
  theme(axis.title = element_text(face="bold"))+
  theme(axis.text = element_text(face="bold"))+
  theme(plot.title = element_text(face="bold"))+
  theme(axis.title.x=element_text(colour="black"))+
  theme(axis.title.y=element_text(colour="black"))+
  theme(axis.text.x=element_text(colour="black"))+
  theme(axis.text.y=element_text(colour="black"))+
  theme(plot.title=element_text(hjust=0.5))+
  theme(strip.text = element_text(size = 6, color = "black"))+
  theme(strip.text = element_text(face = "bold"))
plot_2
ggsave("01_tidyverse_files/figure-html/Sales_by_State_und_Location.png", height = 15 , width = 20)
```

